Analysis of Physical Activity Survey(2022)

### 2022-04-27 outputs/paper/paper.Rmd
Finsihed Model, finishing Results starting discussion points
Finished Results, finishing discussion section

  In section \@ref(Data) we talk about the process of gathering and analyzing the dataset and the variables. Then in the \@ref(Model) section we build a linear model for the rate of obesity. Then in section \@ref(Results) we discuss the implications of the dataset presented. Finally in section \@ref(Discussion) we discuss implications for the United States citizens, as well as the weakness of the study and the further investigation that may be useful to the topic of recreational activity support and physical activity in the United States.

@@

```{r tab2, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means2 <- df_means[order(df_means$V4),]
names(df.means2)[names(df.means2) == 'V2'] <- 'State'
names(df.means2)[names(df.means2) == 'V4'] <- 'Proportion'
df.new <- cbind(df.means2$State,df.means2$Proportion)
knitr::kable(head(df.new),booktabs = TRUE, align = "c", caption = "Excerpt of dataset") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

@@

```{r tab3, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means3 <- df_means[order(df_means$V4, decreasing = T),]
names(df.means3)[names(df.means3) == 'V2'] <- 'State'
names(df.means3)[names(df.means3) == 'V4'] <- 'Proportion'
df.new2 <- cbind(df.means3$State,df.means3$Proportion)
knitr::kable(head(df.new2),booktabs = TRUE, align = "c", caption = "Excerpt of dataset") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

@@

```{r fig2, echo = FALSE, fig.cap = "Bar plot of Obesity by State", fig.width=8,fig.height=8}
### Bar plot of Obesity by State ###
df2 <- subset(df, Year == 2020)
df2 <- subset(df2, Question == "Percent of adults aged 18 years and older who have obesity")
df2 <- df2[order(df2$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df2[i,4],df2[i+1,4],df2[i+2,4],df2[i+3,4],df2[i+4,4],df2[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_m <- cbind(unique(df2$Year),unique(df2$State), unique(df2$Question), round(x, digits = 1))
df_m <- as.data.frame(df_m)
df_l <- melt(df_m[order(df_m$V4),])
p <- ggplot(df_l, aes(x = V2, y = as.numeric(V4), fill = V4)) +scale_y_continuous(limits = c(0,50)) + theme(legend.position="none", axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=0)) + geom_bar(width = 0.8, stat = "identity", position = 'dodge') +
  xlab("State") +
  ylab("Percent of Population")

@@

```{r tab4, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means4 <- df_m[order(df_m$V4),]
names(df.means4)[names(df.means4) == 'V2'] <- 'State'
names(df.means4)[names(df.means4) == 'V4'] <- 'Proportion'
df.new4 <- cbind(df.means4$State,df.means4$Proportion)
knitr::kable(head(df.new4),booktabs = TRUE, align = "c", caption = "Excerpt of Figure 1") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab5, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means5 <- df_m[order(df_m$V4, decreasing = T),]
names(df.means5)[names(df.means5) == 'V2'] <- 'State'
names(df.means5)[names(df.means5) == 'V4'] <- 'Proportion'
df.new5 <- cbind(df.means5$State,df.means5$Proportion)
knitr::kable(head(df.new5),booktabs = TRUE, align = "c", caption = "Excerpt of dataset") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

   Using our model from the

>>>>

  In section \@ref(Data) we talk about the process of gathering and analyzing the dataset and the variables. Then in section \@ref(Model) we build a linear model for the rate of obesity. Then in section \@ref(Results) we discuss the implications of the dataset presented. Finally in section \@ref(Discussion) we discuss implications for the United States citizens, as well as the weakness of the study and the further investigation that may be useful to the topic of recreational activity support and physical activity in the United States.

@@

```{r tab2, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means2 <- df_means[order(df_means$V4),]
names(df.means2)[names(df.means2) == 'V2'] <- 'State'
names(df.means2)[names(df.means2) == 'V4'] <- 'Proportion'
df.new <- cbind(df.means2$State,df.means2$Proportion)
knitr::kable(head(df.new),booktabs = TRUE, align = "c", caption = "Lowest Obesity Rates By State") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

@@

```{r tab3, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means3 <- df_means[order(df_means$V4, decreasing = T),]
names(df.means3)[names(df.means3) == 'V2'] <- 'State'
names(df.means3)[names(df.means3) == 'V4'] <- 'Proportion'
df.new2 <- cbind(df.means3$State,df.means3$Proportion)
knitr::kable(head(df.new2),booktabs = TRUE, align = "c", caption = "Highest Obesity Rates by State") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

@@

```{r fig2, echo = FALSE, fig.cap = "Bar plot of Obesity by State", fig.width=8,fig.height=8}
### Bar plot of Obesity by State ###
df2 <- subset(df, Year == 2019)
df2 <- subset(df2, Question == "Percent of adults aged 18 years and older who have obesity")
df2 <- df2[order(df2$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df2[i,4],df2[i+1,4],df2[i+2,4],df2[i+3,4],df2[i+4,4],df2[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_m <- cbind(unique(df2$Year),unique(df2$State), unique(df2$Question), round(x, digits = 1))
df_m <- as.data.frame(df_m)
df_l <- melt(df_m[order(df_m$V4),])
p <- ggplot(df_l, aes(x = V2, y = as.numeric(V4), fill = V4)) +scale_y_continuous(limits = c(0,50)) + theme(legend.position="none", axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=0)) + geom_bar(width = 0.8, stat = "identity", position = 'dodge') +
  xlab("State") +
  ylab("Percent of Population")

@@

```{r tab4, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means4 <- df_m[order(df_m$V4),]
names(df.means4)[names(df.means4) == 'V2'] <- 'State'
names(df.means4)[names(df.means4) == 'V4'] <- 'Proportion'
df.new4 <- cbind(df.means4$State,df.means4$Proportion)
knitr::kable(head(df.new4),booktabs = TRUE, align = "c", caption = "Lowest Rates of Obesity by State") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab5, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means5 <- df_m[order(df_m$V4, decreasing = T),]
names(df.means5)[names(df.means5) == 'V2'] <- 'State'
names(df.means5)[names(df.means5) == 'V4'] <- 'Proportion'
df.new5 <- cbind(df.means5$State,df.means5$Proportion)
knitr::kable(head(df.new5),booktabs = TRUE, align = "c", caption = "Highest Rates of Obesity by State") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

```{r, echo = FALSE}
### Obesity Rate by State 2020 ###
df8 <- subset(df, Year == 2019)
df8 <- subset(df8, Question == "Percent of adults aged 18 years and older who have obesity")
df8 <- df8[order(df8$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df8[i,4],df8[i+1,4],df8[i+2,4],df8[i+3,4],df8[i+4,4],df8[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df8_means <- cbind(unique(df8$Year),unique(df8$State), unique(df8$Question), round(x, digits = 1))
df8_means <- as.data.frame(df8_means)

df8_no_leisure <- subset(df, Year == 2019)
df8_no_leisure <- subset(df8_no_leisure, Question == "Percent of adults who engage in no leisure-time physical activity")
df8_no_leisure <- df8_no_leisure[order(df8_no_leisure$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df8_no_leisure[i,4],df8_no_leisure[i+1,4],df8_no_leisure[i+2,4],df8_no_leisure[i+3,4],df8_no_leisure[i+4,4],df8_no_leisure[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df8_means_no <- cbind(unique(df8_no_leisure$Year),unique(df8_no_leisure$State), unique(df8_no_leisure$Question), round(x, digits = 1))
df8_means_no <- as.data.frame(df8_means_no)

df8_150 <- subset(df, Year == 2019)
df8_150 <- subset(df8_150, Question == "Percent of adults who achieve at least 150 minutes a week of moderate-intensity aerobic physical activity or 75 minutes a week of vigorous-intensity aerobic activity (or an equivalent combination)")
df8_150 <- df8_150[order(df8_150$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df8_150[i,4],df8_150[i+1,4],df8_150[i+2,4],df8_150[i+3,4],df8_150[i+4,4],df8_150[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df8_means_150 <- cbind(unique(df8_150$Year),unique(df8_150$State), unique(df8_150$Question), round(x, digits = 1))
df8_means_150 <- as.data.frame(df8_means_150)

### Dataframe for muscle strengthening
df8_muscle <- subset(df, Year == 2019)
df8_muscle <- subset(df8_muscle, Question == "Percent of adults who engage in muscle-strengthening activities on 2 or more days a week")
df8_muscle <- df8_muscle[order(df8_muscle$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df8_muscle[i,4],df8_muscle[i+1,4],df8_muscle[i+2,4],df8_muscle[i+3,4],df8_muscle[i+4,4],df8_muscle[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df8_means_muscle <- cbind(unique(df8_muscle$Year),unique(df8_muscle$State), unique(df8_muscle$Question), round(x, digits = 1))
df8_means_muscle <- as.data.frame(df8_means_muscle)
### Test
df.final <- as.data.frame(cbind(df8_means$V2,df8_means$V4,df8_means_150$V4,df8_means_muscle$V4))
Obesity_2019 <- as.numeric(as.vector(df.final$V2))
Aerobics_150min_2019 <- as.numeric(as.vector(df.final$V3))
Muscle_2019 <- as.numeric(as.vector(df.final$V4))
Prediction = 50.5349415+(-0.2690727)*Aerobics_150min_2019+(-0.3223630)*Muscle_2019
```

Below we now look at the proportion of state residents participating in aerobic activities for 150min or more per week as well as the proportion of residents participating in muscle strength training for at least 2 hours per week. We see in Table \@ref(tab:tab10) and Table \@ref(tab:tab11) some familiar states from the Obesity rate Tables \@ref(tab:tab4) and Table \@ref(tab:tab5). Namely Alabama which was one of the highest rates for Obesity in the country also has low rates of Aerobic activity.
```{r tab10, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means4 <- df8_means_150[order(df8_means_150$V4),]
names(df8.means4)[names(df8.means4) == 'V2'] <- 'State'
names(df8.means4)[names(df8.means4) == 'V4'] <- 'Proportion'
df8.new4 <- cbind(df8.means4$State,df8.means4$Proportion)
knitr::kable(head(df8.new4),booktabs = TRUE, align = "c", caption = "States with Lowest rates of Aerobic training") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab11, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means5 <- df8_means_150[order(df8_means_150$V4, decreasing = T),]
names(df8.means5)[names(df8.means5) == 'V2'] <- 'State'
names(df8.means5)[names(df8.means5) == 'V4'] <- 'Proportion'
df8.new5 <- cbind(df8.means5$State,df8.means5$Proportion)
knitr::kable(head(df8.new5),booktabs = TRUE, align = "c", caption = "States with Highest rates of Aerobic training") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

We now look at muscle training in Tables \@ref(tab:tab12) and Table \@ref(tab:tab13). Here we see many of the low obesity rate states from earlier, like Colorado, Florida and the District of Columbia.

```{r tab12, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means6 <- df8_means_muscle[order(df8_means_muscle$V4),]
names(df8.means6)[names(df8.means6) == 'V2'] <- 'State'
names(df8.means6)[names(df8.means6) == 'V4'] <- 'Proportion'
df8.new6 <- cbind(df8.means6$State,df8.means6$Proportion)
knitr::kable(head(df8.new6),booktabs = TRUE, align = "c", caption = "States with Lowest rates of Muscle Training") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab13, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means7 <- df8_means_muscle[order(df8_means_muscle$V4, decreasing = T),]
names(df8.means7)[names(df8.means7) == 'V2'] <- 'State'
names(df8.means7)[names(df8.means7) == 'V4'] <- 'Proportion'
df8.new7 <- cbind(df8.means7$State,df8.means7$Proportion)
knitr::kable(head(df8.new7),booktabs = TRUE, align = "c", caption = "States with Highest rates of Muscle training") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```
The interesting thing here is we see Montana and Vermont both with very high rates of Aerobic Activity, likely attributed to these states being far more rural then the average state, allowing more opportunity for outdoor activities. However again on the low end 
\newpage
